Greenhouse gas emissions model - making scenarios

### 2021-11-10 Scenarios_report.Rmd
update csv
update with the new scenario_mc function

The new `scenario_sampler` function will consist of a wrapper around the `mcSimulation` function, which will be able to modify the input table according to a scenario file we provide. This file will contain information on which variables should be modified for each scenario and how many model runs should be included in the simulation.

```{r scenario_sampler}
scenario_sampler<-function(base_estimate, scenarios, model_function, ..., numberOfModelRuns=NA, randomMethod = "calculate", functionSyntax="data.frameNames",
  relativeTolerance = 0.05,
  verbosity = 0)
{
  initial_estimate = estimate_read_csv(base_estimate)
  scenarios<-read.csv(scenarios)

  scenario_names<-colnames(scenarios[3:ncol(scenarios)])

  for(scens in scenario_names)
  {
    estim<-initial_estimate
    for (i in 2:nrow(scenarios))
    {if(scenarios$param[i]=="both")
      {estim$marginal[scenarios[i,1],"lower"]<-as.numeric(scenarios[i,scens])
       estim$marginal[scenarios[i,1],"upper"]<-as.numeric(scenarios[i,scens])}
     if(scenarios$param[i]=="lower")
       estim$marginal[scenarios[i,1],"lower"]<-as.numeric(scenarios[i,scens])
     if(scenarios$param[i]=="upper")
       estim$marginal[scenarios[i,1],"upper"]<-as.numeric(scenarios[i,scens])
     if(scenarios$param[i]=="distribution")
       estim$marginal[scenarios[i,1],"distribution"]<-scenarios[i,scens]
    }

    if("Runs" %in% scenarios[1,])
      n_Runs<-as.numeric(scenarios[which(scenarios[1,]=="Runs"),scens]) else
        if(!is.na(numberOfModelRuns))
          n_Runs<-numberOfModelRuns else
            stop(paste("Not clear how many times scenario", scens, "should be run"))
      if(!(n_Runs==round(n_Runs))&(n_Runs>0))
        stop(paste("Number of runs for scenario", scens, "is not a positive integer"))
    scen_results<-mcSimulation(
      estimate = estim,
      model_function = model_function,
      ...,
      numberOfModelRuns = n_Runs,
      functionSyntax = functionSyntax)
    scen_results$x[,"Scenario"]<-scens
    scen_results$y[,"Scenario"]<-scens
    if(scens==scenario_names[1])
      end_results<-scen_results
    if(!scens==scenario_names[1])
    {end_results$x<-rbind(end_results$x,scen_results$x)
     end_results$y<-rbind(end_results$y,scen_results$y)
     end_results$call<-"multi-scenario call"
     }

  }
  class(end_results) <- cbind("mcSimulation", class(end_results))
  return(end_results)
}

@@

```{r}
knitr::kable(read.csv("data/scenarios.csv"))

@@

GHG_simulation_scenarios<-scenario_sampler(base_estimate = "data/livestock_ghg_input_table.csv",
                                 scenarios = "data/scenarios.csv",
                                 model_function = ghg_emissions,
                                 functionSyntax = "plainNames")

>>>>

The new `scenario_mc` function consists of a wrapper around the `mcSimulation` function, which is able to modify the input table according to a scenario file we provide. This file contains information on which variables should be modified for each scenario and how many model runs should be included in the simulation.

@@

```{r}
knitr::kable(read.table("data/scenarios.csv", sep = ","))

@@

GHG_simulation_scenarios<-scenario_mc(base_estimate = estimate_read_csv("data/livestock_ghg_input_table.csv"),
                                 scenarios = read.csv("data/scenarios.csv",fileEncoding="UTF-8-BOM"),
                                 model_function = ghg_emissions,
                                 functionSyntax = "plainNames")
